environmental_data_preperation

### 2018-10-26 src/biological_data_prep.Rmd
depth data as per canada, plus time-sliced cell randomisation

```{r}
obs_cell_yymm <- count(data_aea, c("cell_id", "year", "month"))
obs_cell_yymm
write.csv(obs_cell_yymm, file = "../output/bio/no_observations_cell_yymm.csv")
```

>>>>

```{r}
obs_cell_yymm <- count(data_aea, c("cell_id", "year", "month"))
obs_cell_yymm
write.csv(obs_cell_yymm, file = "../output/bio/no_observations_cell_yymm.csv")
```
Now attach these values to data_aea....

total obs for the whole time period
```{r}
data_aea <- merge(data_aea, obs_by_cell, by="cell_id")
head(data_aea)
```
rename freq column to something meaningful

```{r}
names(data_aea)[names(data_aea)=="freq"] <- "total_cell_obs"
head(data_aea)
```

time-sliced
```{r}
data_aea <- merge(data_aea, obs_cell_yymm, by.x=c("cell_id", "year", "month"), by.y=c("cell_id", "year", "month"))
names(data_aea)[names(data_aea)=="freq"] <- "yymm_cell_obs"
head(data_aea)
```

write to .csv
```{r}
write.csv(data_aea,"../output/bio/data_aea_cell_amo_nao_bins_env_depth_cellobno.csv", row.names = FALSE)
```

### 2018-10-26 src/environmental_data_preperation.Rmd
depth data as per canada, plus time-sliced cell randomisation

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
```{r pre-install packages, message=FALSE}
packages <- c("ncdf4", "raster", "rgdal", "useful") 
source("../src/ipak.R")
ipak(packages)
```

@@

note that you will still need to project the bathymetric layer to aea to do the mapping on...

I THINK THIS WILL BE SOLVED ON MY REAL PC - SAM DEAL WITH THIS!

```{r}
library(raster)
mask1 <- "../data/env/aea.tif" #just for canada pc as file isn't loaded
aea <- raster(mask1)
gebco <- raster("../data/env/GEBCO_2014_2D_-70.0_34.0_-43.0_70.0.nc")
gebco
prj <- "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
gebco_aea <- projectRaster(gebco, prj)  
gebco_aea
```

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
```{r pre-install packages, message=FALSE}
packages <- c("ncdf4", "raster", "rgdal", "useful", "marmap") 
source("../src/ipak.R")
ipak(packages)
```

@@

And now create a raster of Gebco in aea for mapping...

```{r}
library(raster)
gebco <- raster("../data/env/GEBCO_2014_2D_-70.0_34.0_-43.0_70.0.nc")
gebco
gebco_aea <- projectRaster(gebco, aea)  
gebco_aea
```
